\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-16 paper.qmd
Added linked plot section

>>>>

## Linked plots

It’s important to access the \gD{} layout and the generated model overlaid on data in \pD{} together to understand whether it fits the points everywhere, fits better in some places, or simply mismatches the pattern. Interactivity also helps in understanding the quirks that occur with different NLDR techniques (XXXXRefer the video after finalising the S-curve).

### 2024-08-16 paper.tex
Added linked plot section

>>>>

\section{Linked plots}\label{linked-plots}

It's important to access the \gD{} layout and the generated model
overlaid on data in \pD{} together to understand whether it fits the
points everywhere, fits better in some places, or simply mismatches the
pattern. Interactivity also helps in understanding the quirks that occur
with different NLDR techniques (XXXXRefer the video after finalising the
S-curve).
